### 2019-04-18 chapters/3-results.tex
mention correlation
correlation tables references

>>>>

Some of the top features were highly correlated between different image types.
See Table~S13 in Supporting Material for Spearman rank correlation coefficients
for the features listed in Tables~2 and~3, calculated across image types. In
addition, Table~S14 contains similar correlation metrics for all feature pairs,
where top five features were taken from each image type.
